---
title: "Adam's Replication Code"
author: "Adam Bear"
date: "4/19/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
source("utilities.R", local = TRUE)
set.seed(123)
theme_set(theme_classic())

# Some constant parameters
nAgents <- 50
nGens <- 10000
```

## Binary Strategy Space

Let's start simulations for strategies that are restricted to 0 or 1, i.e., unbiased with noise vs. biased without noise, respectively.

```{r binary moran}
binary_moran <- evolve(nAgents, nGens, s = 100, strat.round = 0)

pivot_longer(binary_moran, -gen, names_to = "stat") %>% 
  ggplot(aes(gen, value, linetype = stat)) + 
  geom_line(size = .5) + 
  labs(x = "Generation", y = element_blank(), linetype = element_blank()) +
  theme(legend.position = "bottom")
```

Predictably, variance is favored over bias for a simple Moran process. What about if we invert the Moran process?

```{r binary inverted}
binary_inverted <- evolve(nAgents, nGens, s = 100, strat.round = 0, invert = TRUE)

pivot_longer(binary_inverted, -gen, names_to = "stat") %>% 
  ggplot(aes(gen, value, linetype = stat)) + 
  geom_line(size = .2) + 
  labs(x = "Generation", y = element_blank(), linetype = element_blank()) +
  theme(legend.position = "bottom")
```

## Complex Strategy Space

Now we consider 11 possible genotypes between 0 and 1. Here is the normal Moran process.

```{r quintile moran}
quintile_moran <- evolve(nAgents, nGens, s = 100, strat.round = 0)

pivot_longer(quintile_moran, -gen, names_to = "stat") %>% 
  ggplot(aes(gen, value, linetype = stat)) + 
  geom_line(size = .5) + 
  labs(x = "Generation", y = element_blank(), linetype = element_blank()) +
  theme(legend.position = "bottom")
```

And here is the inverted Moran.

```{r quintile inverted}
quintile_inverted <- evolve(nAgents, nGens, s = 100, strat.round = 0, invert = TRUE)

pivot_longer(quintile_inverted, -gen, names_to = "stat") %>% 
  ggplot(aes(gen, value, linetype = stat)) + 
  geom_line(size = .5) + 
  labs(x = "Generation", y = element_blank(), linetype = element_blank()) +
  theme(legend.position = "bottom")
```
