---
title: "risk_survey_compiled_analysis"
author: "Shi Le Wong"
date: "8/15/2020"
output: html_document
---
Downloading Replication Survey Data
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)

library(tidyverse)
library(pander)

panderOptions('digits', 3)
panderOptions('keep.trailing.zeros', TRUE)


# Raw Survey Data
df_raw <- qualtRics::fetch_survey(
  surveyID = "SV_eCJtJv152Bnm873",
  force_request = TRUE,
  verbose = FALSE,
  label = FALSE,
  convert = FALSE
)

df_replication <- df_raw %>% 
  filter( # attention checks
    attn_check_exclude == 0,
    Convexity_11 == -2,
    REI_43 == 0
  ) %>% 
  rename_with(~rei_key$var_name[21:40], REI_23:REI_42) %>% # fix REI names
  rename(Convexity_Total = SC0, Risk_Total = SC1, RI_Total = SC2) %>%
  mutate(RI_Total = RI_Total - 80) # center the NFC measure
```

Downloading Original Risk Survey Data
```{r}
df_raw <- qualtRics::fetch_survey(
  surveyID = "SV_eJ8x8NxuXeB4VjT",
  force_request = TRUE,
  verbose = FALSE,
  label = FALSE,
  convert = FALSE
)

# Key for REI names and reverse coding
# EI = Faith in Intuition; RI = Need for Cognition
rei_key <- read_csv("REI.csv") %>% 
  separate(
    var_name, 
    c("scale", "item_num"),
    sep = "_",
    convert = TRUE,
    remove = FALSE
  ) %>% 
  arrange(scale, item_num) 

df_orig <- df_raw %>% 
  filter( # attention checks
    attn_check_exclude == 0,
    Convexity_11 == -2,
    REI_43 == 0
  ) %>% 
  rename(Convexity_Total = SC0, Risk_Total = SC1, Authoritarianism_Total = SC2) %>% 
  rename_with(~rei_key$var_name, REI_1:REI_42) %>% # fix REI names
  mutate( 
    across( # reverse code the proper EI & RI columns
      rei_key %>% filter(reverse_coded == 1) %>% pull(var_name), 
      ~ -1 * .
    ),
    across( # and reverse code the individualism items
      str_c("individualism_", 8:15),
      ~ -1 * .
    )
  ) %>% 
  rowwise() %>% 
  mutate( # create EI & RI total scores
    EI_Total = sum(c_across(starts_with("EI"))),
    RI_Total = sum(c_across(starts_with("RI"))),
    Individualism_Total = sum(c_across(starts_with("individualism")))
  ) %>% 
  ungroup()
```

Combining both datasets
```{r}
df_combined <- bind_rows(df_orig,df_replication)
```

Correlation between Convexity, Risk and RI
```{r}
df_combined %>% 
  select(Convexity_Total, Risk_Total, RI_Total) %>% 
  drop_na() %>%
  as.matrix() %>% 
  cor() %>% 
  pander()
```

Convexity correlation with Neighborhood (Growing Up)
```{r}
df_combined %>%
  group_by(neighborhood_growup) %>%
  summarize(mean_convexity = mean(Convexity_Total)) %>%
  ungroup() %>%
  ggplot(aes(neighborhood_growup, mean_convexity)) + 
  geom_bar(stat="identity") +
  geom_text(aes(label=sprintf("%0.2f", round(mean_convexity, digits = 2))), vjust=0)
```

Risk correlation with Neighborhood (Growing Up)
```{r}
df_combined %>%
  group_by(neighborhood_growup) %>%
  summarize(mean_risk = mean(Risk_Total)) %>%
  ungroup() %>%
  ggplot(aes(neighborhood_growup, mean_risk)) + 
  geom_bar(stat="identity") +
  geom_text(aes(label=sprintf("%0.2f", round(mean_risk, digits = 2))), vjust=0)
```


Filter by Neighborhood (Urban)
```{r}
df_combined %>% 
  filter(neighborhood_growup == 1) %>%
  select(Convexity_Total, Risk_Total, RI_Total) %>% 
  drop_na() %>%
  as.matrix() %>% 
  cor() %>% 
  pander()
```
Filter by Neighborhood (Suburban)
```{r}
df_combined %>% 
  filter(neighborhood_growup == 2) %>%
  select(Convexity_Total, Risk_Total, RI_Total) %>% 
  drop_na() %>%
  as.matrix() %>% 
  cor() %>% 
  pander()
```

Filter by Neighborhood (Rural)
```{r}
df_combined %>% 
  filter(neighborhood_growup == 3) %>%
  select(Convexity_Total, Risk_Total, RI_Total) %>% 
  drop_na() %>%
  as.matrix() %>% 
  cor() %>% 
  pander()
```

Linear Regression (between all three)
```{r}
lm1 <- lm(formula = Convexity_Total ~ neighborhood_growup + RI_Total, data = df_combined)
summary(lm1)
```

Linear Regression (between Neighborhood and Convexity)
```{r}
lm2 <- lm(formula = Convexity_Total ~ neighborhood_growup, data = df_combined)
summary(lm2)
```

Linear Regression (between Cognition and Convexity)
```{r}
lm3 <- lm(formula = Convexity_Total ~ RI_Total, data = df_combined)
summary(lm3)
```

Linear Regression (between all three, convexity prior)
```{r}
lm4 <- lm(formula = RI_Total ~ Convexity_Total + neighborhood_growup, data = df_combined)
summary(lm4)
```

Linear Regression (between neighborhood and cognition)
```{r}
lm5 <- lm(formula = RI_Total ~ neighborhood_growup, data = df_combined)
summary(lm5)
```

Linear Regression (between convexity and cognition)
```{r}
lm6 <- lm(formula = RI_Total ~ Convexity_Total, data = df_combined)
summary(lm6)
```
